### 2018-07-29 Sections/cloud_quantum_computing.tex
Minor formatting

An alternate fusion strategy is not to directly communicate qubits to be bonded, but instead rely off Bell-pairs provided by a central authority. Each party then applies an EO between their half of the Bell-pair and their target module qubit, which swaps the Bell-pair entanglement onto the two respective module qubits (Sec.~\ref{sec:swapping}).

>>>>

An alternate fusion strategy is not to directly communicate qubits to be bonded, but instead rely off Bell pairs provided by a central authority. Each party then applies an EO between their half of the Bell pair and their target module qubit, which swaps the Bell pair entanglement onto the two respective module qubits (Sec.~\ref{sec:swapping}).

### 2018-07-29 Sections/cryptowars.tex
Minor formatting

E91 is slightly different to BB84. Here Alice and Bob share an entangled Bell-pair provided by a central authority. Then both Alice \textit{and} Bob measure their qubits in random bases. As with BB84, after measuring all qubits, they compare their choices of random bases. When they coincide, they have a shared, random bit. When they don't, they discard their result. From here the remainder of the protocol is the same as for BB84. Thre protocol is summarised in Alg.~\ref{alg:e91}.

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function E91():
\begin{enumerate}
\item A central server shares a Bell-pair between Alice and Bob,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B+\ket{1}_A\ket{1}_B).
\end{align}
\item Alice randomly measures her qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Bob randomly measures his qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Alice and Bob share what their measurement bases were (classically and unencrypted).
\item When Alice and Bob's bases were consistent they store the measurement outcomes as a shared random bit.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{E91\index{E91 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photonic Bell-pairs. Upon completion of the protocol, Alice and Bob share a random bit-string of ruse in a one-time pad cipher\index{One-time pad cipher}.}\label{alg:e91}
\end{table}

@@

An advantage of E91 over BB84 is that it does not require a direct quantum communications link between Alice and Bob. The protocol could be mediated from above by a Bell-pair-producing satellite within line-of-sight of both Alice and Bob.

>>>>

E91 is slightly different to BB84. Here Alice and Bob share an entangled Bell pair provided by a central authority. Then both Alice \textit{and} Bob measure their qubits in random bases. As with BB84, after measuring all qubits, they compare their choices of random bases. When they coincide, they have a shared, random bit. When they don't, they discard their result. From here the remainder of the protocol is the same as for BB84. Thre protocol is summarised in Alg.~\ref{alg:e91}.

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function E91():
\begin{enumerate}
\item A central server shares a Bell pair between Alice and Bob,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B+\ket{1}_A\ket{1}_B).
\end{align}
\item Alice randomly measures her qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Bob randomly measures his qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Alice and Bob share what their measurement bases were (classically and unencrypted).
\item When Alice and Bob's bases were consistent they store the measurement outcomes as a shared random bit.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{E91\index{E91 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photonic Bell pairs. Upon completion of the protocol, Alice and Bob share a random bit-string of ruse in a one-time pad cipher\index{One-time pad cipher}.}\label{alg:e91}
\end{table}

@@

An advantage of E91 over BB84 is that it does not require a direct quantum communications link between Alice and Bob. The protocol could be mediated from above by a Bell pair-producing satellite within line-of-sight of both Alice and Bob.

### 2018-07-29 Sections/entanglement_the_ultimate_quantum_resource.tex
Minor formatting

Foremost, Bell-pairs (Sec.~\ref{sec:bell_state_res}) -- the simplest entangled states -- are an utterly indispensable resource for countless quantum protocols. In brief, Bell-pairs find applicability in, amongst many others, the following key protocols:
\begin{itemize}
\item Cluster states (Sec.~\ref{sec:CSQC})\index{Cluster states}: a Bell-pair is also a 2-qubit cluster state, a supply of which can be employed in fusion strategies to prepare larger cluster states, enabling universal, distributed MBQC.
\item Quantum state teleportation (Sec.~\ref{sec:teleport})\index{Quantum state teleportation}: a shared Bell-pair between Alice and Bob forms the elementary quantum resource upon which the state teleportation protocol is constructed.
\item QKD (Sec.~\ref{sec:QKD})\index{Quantum key distribution}: the E91 QKD\index{E91 QKD protocol} protocol is built upon a reliable stream of distributed Bell-pairs, enabling private communication with perfect information theoretic security.
\item Modularised quantum computation (Sec.~\ref{sec:module})\index{Modularised quantum computation}: using Bell-pairs, entanglement swapping (Sec.~\ref{sec:swapping})\index{Entanglement swapping} can be employed to fuse neighbouring, but potentially distant modules together using operations local to each module.
\item Superdense coding (Sec.~\ref{sec:superdense})\index{Superdense coding}: a shared Bell-pair enables the communication of two classical bits of information via transmission of a single qubit, thereby doubling classical channel capacity\index{Channel capacity}.
\end{itemize}

We see that Bell-pairs form a ubiquitous resource, covering many of the most significant quantum protocols in quantum computation, distributed quantum computation, quantum state teleportation, and quantum cryptography.

@@

Beyond Bell-pairs, multi-qubit GHZ states\index{GHZ state} (Sec.~\ref{sec:GHZ_states}) (the direct generalisation of Bell-pairs to $n$ qubits) are useful in a variety of settings.

For the purposes of quantum anonymous broadcasting\index{Quantum anonymous broadcasting} (Sec.~\ref{sec:anon_broad}), multi-party GHZ entanglement is the primitive resource upon which the cryptographic protocol is constructed. As with Bell-pairs, GHZ states are a known state and infinitely reproducible. They can also be purified. Thus, GHZ entanglement distribution is another useful primitive, which future quantum hubs might specialise in preparing and distributing.

@@

These observations warrant special treatment of entanglement distribution as a fundamental building block in the quantum era. One might envisage a quantum internet in which a central server(s), who specialises in only entangled state preparation and distribution, serves the sole role of pumping out Bell-pairs or other entangled states across the quantum internet to whomever requests them, who subsequently use them for protocols such as those mentioned above. This could be in the form of a server transmitting over fibre networks, across free-space, or via a satellite in orbit, transmitting at an intercontinental level.

What's the advantage of this approach to quantum networking? Why specialise in entanglement distribution, rather than implementing more capable networks with the ability to perform arbitrary operations? There are numerous:
\begin{enumerate}
\item Dedicated servers can specialise in this one particular task, as can be the transmission infrastructure.
\item The entanglement servers are entirely passive, not involved interactively with clients.
\item The server needn't concern itself with the nitty-gritty of the protocols implemented by the end-user. It acts purely as a provider of a single resource, remaining uninvolved in their subsequent applications.
\item Because servers are providing a single standardised product, they can be commodified, enabling mass production of the hardware devices and the associated economy of scale. For example, mass production of simple ground-based Bell state relays, or the construction of a comprehensive globe-enveloping constellation of satellites, would inevitably improve economies of scale.
\item Unlike generic quantum states, Bell-pairs, GHZ states and cluster states are known states that are infinitely reproducible, without having to worry about no-cloning\index{No-cloning theorem} limitations.
\item Photonic Bell-pairs are easily prepared via type-II SPDC at very high repetition rates (\mbox{$\sim 100$MHz-1GHz}), enabling rapid state preparation.
\item Small entangled states like Bell-pairs are relatively `cheap' to prepare, and can be readily manufactured using widely accessible, present-day technology that has already been well-demonstrated on Earth and in space \cite{???}.
\item QoS is a lesser issue in most scenarios. We can employ a \textsc{Send-and-forget}\index{Send-and-forget strategy} protocol for the distribution of entanglement (much like classical UDP\index{User Datagram Protocol}) -- since every state is identical, we needn't be concerned about missing ones. Instead, we can simply wait for the next one (a \textsc{Repeat-until-success}\index{Repeat-until-success strategy} strategy), knowing it will be exactly the same. We also call this the \textsc{Shotgun}\index{Shotgun state preparation} approach -- keep firing away until we hit something, and if we lose a few, who cares?
\item Rather than transmitting quantum states between distant parties directly, if we instead use state teleportation (Sec.~\ref{sec:teleport}) mediated by Bell states, the state to be transmitted will not be corrupted if the communications channel fails (e.g via loss). Instead we can wait for the next successfully transmitted Bell-pair until we are ready to teleport the state, which then proceeds without directly utilising the quantum communications channel, accumulating its associated costs, or risking losing the state altogether should link failure occur. Only classical communication is required to complete the protocol, which can be regarded as error-free for all intents and purposes.
\item Entanglement purification may be employed by parties to improve the cost metrics associated with their shared entanglement, thereby partially overcoming the limitations imposed by the quantum communication channels.
\item If no direct link exists between server and clients, bootstrapped entanglement swapping can be employed to concatenate servers to create longer-distance `virtual' links. This is the basis for \textit{quantum repeater networks}, to be discussed next in Sec.~\ref{sec:rep_net}.
\end{enumerate}

@@

So which ought our quantum hubs specialise in, entanglement distribution, entangling measurements, or both? For most practical purposes the former is far more powerful and robust. Let us take the example of fusing two remote cluster states together to form a larger, distributed virtual cluster. Imagine that their fusion operations are optically mediated by a satellite overhead. The options for satellite-mediated state fusion are (see Fig.~\ref{fig:sat_up_down}):
\begin{itemize}
	\item Downlink mode\index{Satellite downlink} --- The satellite uses the downlink to distribute an entangled Bell-pair between the two nodes. Each node performs a Bell projection between their half of the Bell-pair and their respective qubit from their local cluster state, thereby swapping the entanglement and creating a link. See Fig.~\ref{fig:sat_up_down}(a).
	\item Uplink mode\index{Satellite uplink} --- Each node takes an optical qubit from their cluster state (or entangles their cluster state qubit with an optical qubit), which is uplinked to the satellite. The satellite performs a Bell projection between the two received optical qubits, thereby implementing entanglement swapping between the two nodes, creating a link. See Fig.~\ref{fig:sat_up_down}(b).
\end{itemize}

@@

This yields several key advantages in favour of entanglement distribution as opposed to server-side joint entangling measurements:
\begin{enumerate}
	\item The challenging prospect of quantum memory may operate on Earth, far less onerous and expensive than incorporating this technology into a satellite in low-Earth orbit.
	\item Because the server is not storing any qubits in quantum memory, it does not suffer downtime associated with the periods between receiving the first photon and waiting for the second -- it can continue to spit out Bell-pairs at maximum capacity.
	\item The satellite remains passive, implementing only the simplest of possible operations, reducing mass-production costs.
	\item The satellite does not require any interaction with its clients (classical or quantum).
	\item Because Bell-pairs are known, infinitely reproducible states, the server can operate in a UDP-like\index{UDP} mode and it is not problematic if any given pair was lost. In the reverse direction, loss of a qubit could compromise the entire peripheral state associated with it in the ground statio.
	\item Entanglement purification can be employed to enhance the effective quality of the transmission channel.x
\end{enumerate}

>>>>

Foremost, Bell pairs (Sec.~\ref{sec:bell_state_res}) -- the simplest entangled states -- are an utterly indispensable resource for countless quantum protocols. In brief, Bell pairs find applicability in, amongst many others, the following key protocols:
\begin{itemize}
\item Cluster states (Sec.~\ref{sec:CSQC})\index{Cluster states}: a Bell pair is also a 2-qubit cluster state, a supply of which can be employed in fusion strategies to prepare larger cluster states, enabling universal, distributed MBQC.
\item Quantum state teleportation (Sec.~\ref{sec:teleport})\index{Quantum state teleportation}: a shared Bell pair between Alice and Bob forms the elementary quantum resource upon which the state teleportation protocol is constructed.
\item QKD (Sec.~\ref{sec:QKD})\index{Quantum key distribution}: the E91 QKD\index{E91 QKD protocol} protocol is built upon a reliable stream of distributed Bell pairs, enabling private communication with perfect information theoretic security.
\item Modularised quantum computation (Sec.~\ref{sec:module})\index{Modularised quantum computation}: using Bell pairs, entanglement swapping (Sec.~\ref{sec:swapping})\index{Entanglement swapping} can be employed to fuse neighbouring, but potentially distant modules together using operations local to each module.
\item Superdense coding (Sec.~\ref{sec:superdense})\index{Superdense coding}: a shared Bell pair enables the communication of two classical bits of information via transmission of a single qubit, thereby doubling classical channel capacity\index{Channel capacity}.
\end{itemize}

We see that Bell pairs form a ubiquitous resource, covering many of the most significant quantum protocols in quantum computation, distributed quantum computation, quantum state teleportation, and quantum cryptography.

@@

Beyond Bell pairs, multi-qubit GHZ states\index{GHZ state} (Sec.~\ref{sec:GHZ_states}) (the direct generalisation of Bell pairs to $n$ qubits) are useful in a variety of settings.

For the purposes of quantum anonymous broadcasting\index{Quantum anonymous broadcasting} (Sec.~\ref{sec:anon_broad}), multi-party GHZ entanglement is the primitive resource upon which the cryptographic protocol is constructed. As with Bell pairs, GHZ states are a known state and infinitely reproducible. They can also be purified. Thus, GHZ entanglement distribution is another useful primitive, which future quantum hubs might specialise in preparing and distributing.

@@

These observations warrant special treatment of entanglement distribution as a fundamental building block in the quantum era. One might envisage a quantum internet in which a central server(s), who specialises in only entangled state preparation and distribution, serves the sole role of pumping out Bell pairs or other entangled states across the quantum internet to whomever requests them, who subsequently use them for protocols such as those mentioned above. This could be in the form of a server transmitting over fibre networks, across free-space, or via a satellite in orbit, transmitting at an intercontinental level.

What's the advantage of this approach to quantum networking? Why specialise in entanglement distribution, rather than implementing more capable networks with the ability to perform arbitrary operations? There are numerous:
\begin{enumerate}
\item Dedicated servers can specialise in this one particular task, as can be the transmission infrastructure.
\item The entanglement servers are entirely passive, not involved interactively with clients.
\item The server needn't concern itself with the nitty-gritty of the protocols implemented by the end-user. It acts purely as a provider of a single resource, remaining uninvolved in their subsequent applications.
\item Because servers are providing a single standardised product, they can be commodified, enabling mass production of the hardware devices and the associated economy of scale. For example, mass production of simple ground-based Bell state relays, or the construction of a comprehensive globe-enveloping constellation of satellites, would inevitably improve economies of scale.
\item Unlike generic quantum states, Bell pairs, GHZ states and cluster states are known states that are infinitely reproducible, without having to worry about no-cloning\index{No-cloning theorem} limitations.
\item Photonic Bell pairs are easily prepared via type-II SPDC at very high repetition rates (\mbox{$\sim 100$MHz-1GHz}), enabling rapid state preparation.
\item Small entangled states like Bell pairs are relatively `cheap' to prepare, and can be readily manufactured using widely accessible, present-day technology that has already been well-demonstrated on Earth and in space \cite{???}.
\item QoS is a lesser issue in most scenarios. We can employ a \textsc{Send-and-forget}\index{Send-and-forget strategy} protocol for the distribution of entanglement (much like classical UDP\index{User Datagram Protocol}) -- since every state is identical, we needn't be concerned about missing ones. Instead, we can simply wait for the next one (a \textsc{Repeat-until-success}\index{Repeat-until-success strategy} strategy), knowing it will be exactly the same. We also call this the \textsc{Shotgun}\index{Shotgun state preparation} approach -- keep firing away until we hit something, and if we lose a few, who cares?
\item Rather than transmitting quantum states between distant parties directly, if we instead use state teleportation (Sec.~\ref{sec:teleport}) mediated by Bell states, the state to be transmitted will not be corrupted if the communications channel fails (e.g via loss). Instead we can wait for the next successfully transmitted Bell pair until we are ready to teleport the state, which then proceeds without directly utilising the quantum communications channel, accumulating its associated costs, or risking losing the state altogether should link failure occur. Only classical communication is required to complete the protocol, which can be regarded as error-free for all intents and purposes.
\item Entanglement purification may be employed by parties to improve the cost metrics associated with their shared entanglement, thereby partially overcoming the limitations imposed by the quantum communication channels.
\item If no direct link exists between server and clients, bootstrapped entanglement swapping can be employed to concatenate servers to create longer-distance `virtual' links. This is the basis for \textit{quantum repeater networks}, to be discussed next in Sec.~\ref{sec:rep_net}.
\end{enumerate}

@@

So which ought our quantum hubs specialise in, entanglement distribution, entangling measurements, or both? For most practical purposes the former is far more powerful and robust. Let us take the example of fusing two remote cluster states together to form a larger, distributed virtual cluster. Imagine that their fusion operations are optically mediated by a satellite overhead. The options for satellite-mediated state fusion are (see Fig.~\ref{fig:sat_up_down}):
\begin{itemize}
	\item Downlink mode\index{Satellite downlink} --- The satellite uses the downlink to distribute an entangled Bell pair between the two nodes. Each node performs a Bell projection between their half of the Bell pair and their respective qubit from their local cluster state, thereby swapping the entanglement and creating a link. See Fig.~\ref{fig:sat_up_down}(a).
	\item Uplink mode\index{Satellite uplink} --- Each node takes an optical qubit from their cluster state (or entangles their cluster state qubit with an optical qubit), which is uplinked to the satellite. The satellite performs a Bell projection between the two received optical qubits, thereby implementing entanglement swapping between the two nodes, creating a link. See Fig.~\ref{fig:sat_up_down}(b).
\end{itemize}

@@

This yields several key advantages in favour of entanglement distribution as opposed to server-side joint entangling measurements:
\begin{enumerate}
	\item The challenging prospect of quantum memory may operate on Earth, far less onerous and expensive than incorporating this technology into a satellite in low-Earth orbit.
	\item Because the server is not storing any qubits in quantum memory, it does not suffer downtime associated with the periods between receiving the first photon and waiting for the second -- it can continue to spit out Bell pairs at maximum capacity.
	\item The satellite remains passive, implementing only the simplest of possible operations, reducing mass-production costs.
	\item The satellite does not require any interaction with its clients (classical or quantum).
	\item Because Bell pairs are known, infinitely reproducible states, the server can operate in a UDP-like\index{UDP} mode and it is not problematic if any given pair was lost. In the reverse direction, loss of a qubit could compromise the entire peripheral state associated with it in the ground statio.
	\item Entanglement purification can be employed to enhance the effective quality of the transmission channel.x
\end{enumerate}

### 2018-07-29 Sections/interconnecting_and_interfacing_quantum_networks.tex
Minor formatting

Atomic ensembles are essentially well-engineered clouds of atomic gasses, trapped in a glass container, coupled to an optical mode. Atomic ensembles have been demonstrated with extremely long coherence lifetimes ($\tau_2\approx$100ms \comment{Check this!}\index{$\tau_2$ time}), operating at room temperatures (a very attractive feature on its own). They exhibit \textit{collective enhancement}\index{Collective enhancement} in their coupling to the optical mode -- the optical coupling strength is amplified by a factor quadratic in $N$ compared to single-atom optical coupling, mitigating the need for a cavity.

>>>>

Atomic ensembles are essentially well-engineered clouds of atomic gasses, trapped in a glass container, coupled to an optical mode. Atomic ensembles have been demonstrated with extremely long coherence lifetimes ($T_2\approx$100ms \comment{Check this!}\index{$T_2$ time}), operating at room temperatures (a very attractive feature on its own). They exhibit \textit{collective enhancement}\index{Collective enhancement} in their coupling to the optical mode -- the optical coupling strength is amplified by a factor quadratic in $N$ compared to single-atom optical coupling, mitigating the need for a cavity.

### 2018-07-29 Sections/physical_architectures_for_quantum_computing.tex
Added all dropcaps
Minor formatting

The models for quantum computation introduced in the previous section are abstractions of algorithms in terms of elementary operations. But elementary operations must ultimately be physically realised. There are countless physical architectures for realising quantum computations, far too many to describe here, each with their own advantages and disadvantages, and it is far from clear which physical architecture(s) will ultimately win the quantum race.

@@

%
% Bell-Pairs
%

\subsubsection{Bell-pairs}\index{Bell-pairs}\label{sec:CV_bell_pairs}

In the squeezed basis one can prepare Bell-pairs in an analogous manner to doing so using single-photon encoding. Namely, mixing two orthogonally squeezed states (squeezed and anti-squeezed states) on a 50:50 beamsplitter generates Bell-type entanglement. This is shown in Fig.~\ref{fig:CV_bell_pair}.

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{CV_bell_pair}
\caption{Preparation of a CV Bell-pair using a 50:50 beamsplitter to entangled two  squeezed states, squeezed in orthogonal directions in phase-space.}\label{fig:CV_bell_pair}	
\end{figure}

@@

Using a 50:50 beamsplitter to implement the reverse of Bell-pair preparation (described previously in Sec.~\ref{sec:CV_bell_pairs}), one can construct a Bell analyser for performing projections in the Bell basis\index{Bell projections}.

@@

\begin{figure}[!htb]
\includegraphics[width=0.375\textwidth]{barrett_kok}
\caption{Two atomic systems in $\lambda$-configurations, each coupled with an optical mode. An EO between them is mediated via linear optics which-path erasure. Each system contains two degenerate ground states, which jointly encode a qubit (\mbox{$\ket{0}\equiv\ket{\!\uparrow}$}, \mbox{$\ket{1}\equiv\ket{\!\downarrow}$}), and an additional excited state ($\ket{e}$), which only couples to the $\ket{\!\downarrow}$ state. A $\pi$-pulse excites the electron from the $\ket{\!\downarrow}$ to the $\ket{e}$ state, after which emission of a photon is associated with a coherent relaxation back to $\ket{\!\downarrow}$. If the two optical modes are interfered on a 50:50 beamsplitter, and a single photon is detected between the two photo-detectors, $D_1$ and $D_2$, the two emission processes become indistinguishable, and which-path erasure entangles the two qubits by projecting them onto a maximally entangled Bell-pair. More complicated networks based on this EO allow the preparation of cluster states, enabling universal quantum computation. In a quantum networking context, the matter qubits could be held by a client, and the optical interferometry implementing the computation outsourced to the cloud, i.e the PBS, $D_1$ and $D_2$ are implemented in the cloud. This would also facilitate the preparation of shared entangled states, where different clients possess parts of an entangled state, potentially physically separated over long distances.} \label{fig:barrett_kok}
\end{figure}

@@

Alternately, if there is no direct line of quantum communication between two qubits, an EO can be performed by directly employing the same idea in reverse. We imagine that a third party, such as a satellite, acts as a server for entangled Bell-pairs. Two parties receive one qubit each from the pair. Then they perform an EO between their halves of the Bell-pair and their local qubits. With appropriate local corrections, mediated by only cheap classical communication, this teleports the action of an EO onto the two qubits, creating a link between them.

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function WhichPathErasure():
\begin{enumerate}
\item Alice and Bob each prepare an equal superposition of the two logical basis states,
\begin{align}
\ket\psi_\mathrm{in} = &\frac{1}{2}(\ket{\!\uparrow}_{A_1}+\ket{\!\downarrow}_{A_1})\ket{0}_{A_2}\nonumber \\
&\cdot (\ket{\!\uparrow}_{B_1}+\ket{\!\downarrow}_{B_1})\ket{0}_{B_2},
\end{align}
where $A_1/B_1$ denote the matter qubits, and $A_2/B_2$ denote their coupled optical modes.
\item Apply a $\pi$-pulse to each qubit, inducing a \mbox{$\ket{\!\downarrow}\to\ket{e}$} transition,
\begin{align}
\ket\psi_\pi = \hat{U}_\pi\ket\psi_\mathrm{in} = &\frac{1}{2}(\ket{\!\uparrow}_{A_1}+\ket{e}_{A_1})\ket{0}_{A_2}\nonumber \\
&\cdot (\ket{\!\uparrow}_{B_1}+\ket{e}_{B_1})\ket{0}_{B_2}.
\end{align}
\item Wait for a coherent relaxation, inducing the transition \mbox{$\ket{e}\to\ket{\!\downarrow}\hat{a}^\dag$}, which emits a single photon,
\begin{align}
\ket\psi_\mathrm{relax} = \hat{U}_\mathrm{relax}\ket\psi_\pi = &\frac{1}{2}(\ket{\!\uparrow}_{A_1}+\ket{\!\downarrow}_{A_1}\hat{a}^\dag_{A_2})\ket{0}_{A_2}\nonumber \\
&\cdot (\ket{\!\uparrow}_{B_1}+\ket{\!\downarrow}_{B_1}\hat{a}^\dag_{B_2})\ket{0}_{B_2}.
\end{align}
\item Apply a 50:50 beamsplitter between the two optical modes,
\begin{align}
\ket\psi_\mathrm{BS} = \hat{U}_\mathrm{BS} \ket\psi_\mathrm{relax} = &\frac{1}{2}(\ket{\!\uparrow}_{A_1}+\ket{\!\downarrow}_{A_1}[\hat{a}^\dag_{A_2}+\hat{a}^\dag_{B_2}])\nonumber \\
&\cdot (\ket{\!\uparrow}_{B_1}+\ket{\!\downarrow}_{B_1}[\hat{a}^\dag_{A_2}-\hat{a}^\dag_{B_2}])\nonumber \\
&\cdot \ket{0}_{A_2}\ket{0}_{B_2}.
\end{align}
\item Conditional upon detecting exactly one photon between the output optical modes, we obtain,
\begin{align}
\ket\psi_\mathrm{out}^{1,0} = \bra{1,0}_{A_2,B_2} \ket\psi_\mathrm{BS} = \frac{1}{2} (\ket{\!\uparrow,\downarrow}_{A_1,B_1} + \ket{\!\downarrow,\uparrow}_{A_1,B_1}), \nonumber \\
\ket\psi_\mathrm{out}^{0,1} = \bra{0,1}_{A_2,B_2} \ket\psi_\mathrm{BS} = \frac{1}{2} (\ket{\!\uparrow,\downarrow}_{A_1,B_1} - \ket{\!\downarrow,\uparrow}_{A_1,B_1}),
\end{align}
which is a Bell-pair between the matter qubits.
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{Using which-path erasure to entangle two $\lambda$-configuration matter qubits via post-selected linear optics. Note that the two matter qubits could in principle be arbitrarily physically separated. Only the emitted photons need be brought together locally for the implementation of a beamsplitter operation. This lends such entanglement generation protocols to distributed implementation.} \label{alg:which_path}
\end{table}

>>>>

\dropcap{T}{he} models for quantum computation introduced in the previous section are abstractions of algorithms in terms of elementary operations. But elementary operations must ultimately be physically realised. There are countless physical architectures for realising quantum computations, far too many to describe here, each with their own advantages and disadvantages, and it is far from clear which physical architecture(s) will ultimately win the quantum race.

@@

%
% Bell pairs
%

\subsubsection{Bell pairs}\index{Bell pairs}\label{sec:CV_bell_pairs}

In the squeezed basis one can prepare Bell pairs in an analogous manner to doing so using single-photon encoding. Namely, mixing two orthogonally squeezed states (squeezed and anti-squeezed states) on a 50:50 beamsplitter generates Bell-type entanglement. This is shown in Fig.~\ref{fig:CV_bell_pair}.

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{CV_bell_pair}
\caption{Preparation of a CV Bell pair using a 50:50 beamsplitter to entangled two  squeezed states, squeezed in orthogonal directions in phase-space.}\label{fig:CV_bell_pair}	
\end{figure}

@@

Using a 50:50 beamsplitter to implement the reverse of Bell pair preparation (described previously in Sec.~\ref{sec:CV_bell_pairs}), one can construct a Bell analyser for performing projections in the Bell basis\index{Bell projections}.

@@

\begin{figure}[!htb]
\includegraphics[width=0.375\textwidth]{barrett_kok}
\caption{Two atomic systems in $\lambda$-configurations, each coupled with an optical mode. An EO between them is mediated via linear optics which-path erasure. Each system contains two degenerate ground states, which jointly encode a qubit (\mbox{$\ket{0}\equiv\ket{\!\uparrow}$}, \mbox{$\ket{1}\equiv\ket{\!\downarrow}$}), and an additional excited state ($\ket{e}$), which only couples to the $\ket{\!\downarrow}$ state. A $\pi$-pulse excites the electron from the $\ket{\!\downarrow}$ to the $\ket{e}$ state, after which emission of a photon is associated with a coherent relaxation back to $\ket{\!\downarrow}$. If the two optical modes are interfered on a 50:50 beamsplitter, and a single photon is detected between the two photo-detectors, $D_1$ and $D_2$, the two emission processes become indistinguishable, and which-path erasure entangles the two qubits by projecting them onto a maximally entangled Bell pair. More complicated networks based on this EO allow the preparation of cluster states, enabling universal quantum computation. In a quantum networking context, the matter qubits could be held by a client, and the optical interferometry implementing the computation outsourced to the cloud, i.e the PBS, $D_1$ and $D_2$ are implemented in the cloud. This would also facilitate the preparation of shared entangled states, where different clients possess parts of an entangled state, potentially physically separated over long distances.} \label{fig:barrett_kok}
\end{figure}

@@

Alternately, if there is no direct line of quantum communication between two qubits, an EO can be performed by directly employing the same idea in reverse. We imagine that a third party, such as a satellite, acts as a server for entangled Bell pairs. Two parties receive one qubit each from the pair. Then they perform an EO between their halves of the Bell pair and their local qubits. With appropriate local corrections, mediated by only cheap classical communication, this teleports the action of an EO onto the two qubits, creating a link between them.

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function WhichPathErasure():
\begin{enumerate}
\item Alice and Bob each prepare an equal superposition of the two logical basis states,
\begin{align}
\ket\psi_\mathrm{in} = &\frac{1}{2}(\ket{\!\uparrow}_{A_1}+\ket{\!\downarrow}_{A_1})\ket{0}_{A_2}\nonumber \\
&\cdot (\ket{\!\uparrow}_{B_1}+\ket{\!\downarrow}_{B_1})\ket{0}_{B_2},
\end{align}
where $A_1/B_1$ denote the matter qubits, and $A_2/B_2$ denote their coupled optical modes.
\item Apply a $\pi$-pulse to each qubit, inducing a \mbox{$\ket{\!\downarrow}\to\ket{e}$} transition,
\begin{align}
\ket\psi_\pi = \hat{U}_\pi\ket\psi_\mathrm{in} = &\frac{1}{2}(\ket{\!\uparrow}_{A_1}+\ket{e}_{A_1})\ket{0}_{A_2}\nonumber \\
&\cdot (\ket{\!\uparrow}_{B_1}+\ket{e}_{B_1})\ket{0}_{B_2}.
\end{align}
\item Wait for a coherent relaxation, inducing the transition \mbox{$\ket{e}\to\ket{\!\downarrow}\hat{a}^\dag$}, which emits a single photon,
\begin{align}
\ket\psi_\mathrm{relax} = \hat{U}_\mathrm{relax}\ket\psi_\pi = &\frac{1}{2}(\ket{\!\uparrow}_{A_1}+\ket{\!\downarrow}_{A_1}\hat{a}^\dag_{A_2})\ket{0}_{A_2}\nonumber \\
&\cdot (\ket{\!\uparrow}_{B_1}+\ket{\!\downarrow}_{B_1}\hat{a}^\dag_{B_2})\ket{0}_{B_2}.
\end{align}
\item Apply a 50:50 beamsplitter between the two optical modes,
\begin{align}
\ket\psi_\mathrm{BS} = \hat{U}_\mathrm{BS} \ket\psi_\mathrm{relax} = &\frac{1}{2}(\ket{\!\uparrow}_{A_1}+\ket{\!\downarrow}_{A_1}[\hat{a}^\dag_{A_2}+\hat{a}^\dag_{B_2}])\nonumber \\
&\cdot (\ket{\!\uparrow}_{B_1}+\ket{\!\downarrow}_{B_1}[\hat{a}^\dag_{A_2}-\hat{a}^\dag_{B_2}])\nonumber \\
&\cdot \ket{0}_{A_2}\ket{0}_{B_2}.
\end{align}
\item Conditional upon detecting exactly one photon between the output optical modes, we obtain,
\begin{align}
\ket\psi_\mathrm{out}^{1,0} = \bra{1,0}_{A_2,B_2} \ket\psi_\mathrm{BS} = \frac{1}{2} (\ket{\!\uparrow,\downarrow}_{A_1,B_1} + \ket{\!\downarrow,\uparrow}_{A_1,B_1}), \nonumber \\
\ket\psi_\mathrm{out}^{0,1} = \bra{0,1}_{A_2,B_2} \ket\psi_\mathrm{BS} = \frac{1}{2} (\ket{\!\uparrow,\downarrow}_{A_1,B_1} - \ket{\!\downarrow,\uparrow}_{A_1,B_1}),
\end{align}
which is a Bell pair between the matter qubits.
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{Using which-path erasure to entangle two $\lambda$-configuration matter qubits via post-selected linear optics. Note that the two matter qubits could in principle be arbitrarily physically separated. Only the emitted photons need be brought together locally for the implementation of a beamsplitter operation. This lends such entanglement generation protocols to distributed implementation.} \label{alg:which_path}
\end{table}
